Finite-size scaling of free energy in the dimer model on a hexagonal domain

### 2019-04-04 AffineLieAlgebras/MQFT2018/paper.tex
New computation is completed, numeric section started

For $\left.f\right|_{\varepsilon\to 0}$ we have $\chi(0)=1$ and the sum $\sum_{n=1}^{\infty}
\frac{H_{n}}{n^{3}}$ is just a sum of  polylogarithms
$\mathrm{Li}_{s}(z)=\sum_{n=1}^{\infty}\frac{z^{n}}{n^{s}}$ of third order:
\begin{equation}
  \label{eq:42}
  \left.f\right|_{\varepsilon\to 0} =\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
    \Li_{3}(e^{-a-b})\right.\\
  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
\end{equation}
The derivative of the function $\chi(z)$ is zero, $\chi'(0)=0$, and the series
$\sum_{n=1}^{\infty} \frac{\chi'(n\varepsilon)}{n^{2}}H_{n}$ are convergent for a finite
$\varepsilon$, thus we have for a derivative
\begin{equation}
  \label{eq:43}
\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}=0
\end{equation}

@@

First sum in the expression \eqref{eq:46} can be expressed as follows. First, consider second
derivative of $\chi(z)$, separate an exponent and denote what is left by $\xi(z)$:
\begin{equation}
  \label{eq:48}
  \chi''(z)=e^{-z}\frac{e^{2 z} \left(z^2+4 e^z
   \left(z^2-1\right)+e^{2 z} \left(z^2-4
   z+2\right)+4
   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z)
\end{equation}
The sum is then rewritten
\begin{equation}
  \label{eq:49}
  \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}=
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}   
\end{equation}
The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}}\right)\approx \ln
\varepsilon$,
the second term can approximated by the integral:
\begin{equation}
  \label{eq:50}
  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
\end{equation}

Thus we arrive to the following asymptotic behavior of the free energy:

In general, the behavior of the form
$f=f_{0}+f_{1}\varepsilon+f_{2} \varepsilon^{2}\ln \varepsilon+f_{3}\varepsilon^{2}$ is expected in
two-dimensional critical systems \cite{cardy1988finite}.

Here and below we will use the notation:
\begin{equation}
  \label{eq:5}
  g(x,y,z)=\frac{1}{e^{x+y+z}-1}
\end{equation}

Omitting the arguments of $g(i\varepsilon,j\varepsilon,k\varepsilon)$ we thus can rewrite the free energy as
\begin{equation}
  \label{eq:2}
  f=-\frac{1}{V}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \left[\ln\left(1+g-g e^{\varepsilon}\right)-\ln\left(1+g-g e^{2\varepsilon}\right)\right]
\end{equation}
We have $V=2(MN+MK+NK)=2(ab+bc+ca)\varepsilon^{-2}$ and $g\sim \varepsilon^{-1}$ as
$\varepsilon\to 0$. Let us rewrite the logarithms as a series in $\varepsilon, g$:
\begin{equation}
  \label{eq:25}
  f=-\frac{1}{2(ab+bc+ca)}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \varepsilon^{2}
  \left[-\sum_{l=1}^{\infty}\frac{1}{l}\left(\sum_{m=1}^{\infty}\frac{g\varepsilon^{m}}{m!}\right)^{l}+
    \sum_{l=1}^{\infty}\frac{1}{l}\left(\sum_{m=1}^{\infty}\frac{2^{m} g\varepsilon^{m}}{m!}\right)^{l}\right]
\end{equation}
We are interested in the leading contributions in $\varepsilon$. Since $g\sim \varepsilon^{-1}$,
they come from the terms $g^{l}\varepsilon^{l}$ in the square brackets. The coefficients before
these terms are $\frac{2^{l}-1}{l}$:
\begin{equation}
  \label{eq:36}
  f\approx-\frac{1}{2(ab+bc+ca)}\sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \varepsilon^{2} \left[g+\sum_{l=2}^{\infty}\frac{2^{l}-1}{l}g^{l}\varepsilon^{l}\right]
\end{equation}
We separated the first term since it plays a major role in the following computations.

%% Since $g\sim \varepsilon^{-1}$, the first two terms in $\varepsilon$ are
%% \begin{multline}
%% \label{eq:35}
%%   %\frac{f}{T}
%%   f\approx-\frac{1}{2(ab+bc+ca)} \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K}\left\{
%%     \varepsilon^{3} g(i\varepsilon,j\varepsilon,k\varepsilon)+
%%     \frac{3}{2}\varepsilon^{4}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right\}\\
%%   +\mathcal{O}(\varepsilon^{2})
%% \end{multline}
%% Contribution of the order $\varepsilon^{2}$ come from the terms $g^{l}\varepsilon^{l}$ from the square brackets of the equation \eqref{eq:25}. The coefficients before these terms are $\frac{2^{l}-1}{l}$
%% 
%% 
%% \begin{multline}
%%   \label{eq:4}
%%   %\frac{f}{T}
%%   f=- \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}\left\{
%%     \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)+
%%     \frac{3}{2}\varepsilon^{2}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}\right]\right.\\
%%   \left.+\frac{7}{6}\varepsilon^{3}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3 g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+
%%       2 g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}  + \mathcal{O}(\varepsilon^{4})
%% \end{multline}
%% %% Wrong power of $\varepsilon$ below!!
%% 
%% 
This expression looks like a combination of Riemann sums for some integrals. Note that these sums
are finite for each $l$, but some of the corresponding integrals are divergent.

Let $G$ be an analytic function in the cube $[0,a]\times[0,b]\times[0,c]$, then
\begin{multline}
  \label{eq:21}
  \int_{0}^{a} \int_{0}^{b}\int_{0}^{c}G(x,y,z) \dx\; \dy\;
  \dz\approx\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\left\{\varepsilon^{3}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)-\right.\\
  \left.-\left[\frac{\varepsilon^{4}}{2}\left((\partial_{x}+\partial_{y}+\partial_{z})G\right)(i\varepsilon,j\varepsilon,k\varepsilon)\right]+\right.\\
  \left.\varepsilon^{5}\left(\frac{1}{6}(\partial_{x}^{2}+\partial_{y}^{2}+\partial_{z}^{2})+\frac{1}{4}(\partial_{x}\partial_{y}+\partial_{x}\partial_{z}+\partial_{y}\partial_{z})\right)G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)
  \right\}+\mathcal{O}(\varepsilon^{6})
\end{multline}
This formula can be easily derived by dividing the volume of integration into cubes with side
$\varepsilon$ and substituting Taylor series for $G$ into integrals.

We can use this formula to approximate sums by integrals. Similar formula can be written for a
function of two variables and double sums. We will not need higher order terms, but will use the
approximation:
\begin{equation}
\label{eq:8}
  \sum_{j=1}^{N}\sum_{k=1}^{K}\varepsilon^{2}G\left(i\varepsilon,j\varepsilon,k\varepsilon\right)\approx \int_{0}^{b}\int_{0}^{c}G(i\varepsilon,y,z) \dy\; \dz+\mathcal{O}(\varepsilon^{3}))
\end{equation}

Note that
\begin{equation}
  \label{eq:6}
  \begin{array}{c}
    \partial_{x}g(x,y,z)=-g(x,y,z)-g(x,y,z)^{2}\\
    \partial_{x}^{2}g(x,y,z)=g(x,y,z)+3g(x,y,z)^{2}+2g(x,y,z)^{3}
  \end{array}
\end{equation}

Taking this into account and using the relation \eqref{eq:21} to express the triple sum
$ \sum_{i=1}^{M} \sum_{j=1}^{N} \sum_{k=1}^{K} \frac{1}{V}    \varepsilon g(i\varepsilon,j\varepsilon,k\varepsilon)$
in \eqref{eq:4} as the integral plus corrections, we obtain
\begin{multline}
\label{eq:23}
 f=-\frac{1}{2(ab+bc+ca)}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
  \left.+\sum_{i=1}^{M}\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}\left[g(i\varepsilon,j\varepsilon,k\varepsilon)+3
      g(i\varepsilon,j\varepsilon,k\varepsilon)^{2}+2
      g(i\varepsilon,j\varepsilon,k\varepsilon)^{3}\right]\right\}
\end{multline}
Due to the equations \eqref{eq:6}, the corrections are of the same form as the higher order terms in
$\varepsilon$. The linear in $\varepsilon$ term in \eqref{eq:4} is cancelled by three partial
derivatives in \eqref{eq:21}. The coefficient of the quadratic term is changed by the addition of
second derivatives from \eqref{eq:21} to $\frac{1}{12}$.

There is no singularity in the sum, but
$\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{(\exp(x+y+z)-1)^{3}}$ diverges
logarithmically. So we can not just apply the integral representation~\eqref{eq:21} directly.

We apply the formula \eqref{eq:8} to the internal sums in the triple sum, since there is no
singularity in $\frac{1}{\left((\exp(i\varepsilon+j\varepsilon+k\varepsilon)-1\right)^{3}}$ for
$i\neq 0$:

\begin{equation}
  \label{eq:9}
\sum_{i=1}^{M}\left(\sum_{j=1}^{N}\sum_{k=1}^{K}\frac{\varepsilon^{5}}{12}
      \frac{e^{2(i\varepsilon+j\varepsilon+k\varepsilon)}+e^{i\varepsilon+j\varepsilon+k\varepsilon}}{\left(e^{i\varepsilon+j\varepsilon+k\varepsilon}-1\right)^{3}}  \right)\approx
    \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M} \int_{0}^{b}\int_{0}^{c}
      \left(\frac{e^{2(i\varepsilon+y+z)}+e^{i\varepsilon+y+z}}{\left(e^{i\varepsilon+y+z}-1\right)^{3}}\right) \dy \dz+\mathcal{O}(\varepsilon^{3})
\end{equation}

The double integral can be taken explicitly, so we obtain
\begin{equation}
  \label{eq:11}
  \frac{\varepsilon^{3}}{12}\sum_{i=1}^{M}\left(     \frac{1}{e^{b+c+i\varepsilon}-1}+
  \frac{1}{1-e^{b+i\varepsilon}}+\frac{1}{1-e^{c+i\varepsilon}}+\frac{1}{e^{i\varepsilon}-1}\right)
\end{equation}

The function $\frac{1}{e^{x}-1}$ has a divergence, so we can not apply integral approximation directly. We first need to 
subtract and add $\frac{1}{i\varepsilon}$. The sum over $i$ of this term can be approximated using Euler formula:
\begin{equation}
    \label{eq:24}
    \sum_{i=1}^{M}\frac{1}{i}=\frac{1}{M}\sum_{i=1}^{M}\frac{1}{i/M}=\int_{\frac{1}{M}}^{1}\frac{\dx}{x}+\gamma+O(\varepsilon)=-\ln\varepsilon+\ln a+\gamma+O(\varepsilon)
  \end{equation}
Thus we get the integral %%!!!!!
\begin{multline}
  \label{eq:13}
    \frac{\varepsilon^{3}}{12}\left[\sum_{i=1}^{M}\left(     \frac{1}{e^{b+c+i\varepsilon}-1}+
      \frac{1}{1-e^{b+i\varepsilon}}+\frac{1}{1-e^{c+i\varepsilon}}+\frac{1}{e^{i\varepsilon}-1}-\frac{1}{i\varepsilon}\right)-\ln\varepsilon+\ln a+\gamma+\mathcal{O}(\varepsilon^{3})\right]\approx\\
   \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
      \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)\dx-\ln\varepsilon+\ln a+\gamma\right]+\mathcal{O}(\varepsilon^{3})    
\end{multline}
The integral is now taken explicitly, it is equal to
\begin{multline}
  \label{eq:22}
     \frac{\varepsilon^{2}}{12}\left[\int_{0}^{a}\left(     \frac{1}{e^{b+c+x}-1}+
         \frac{1}{1-e^{b+x}}+\frac{1}{1-e^{c+x}}+\frac{1}{e^{x}-1}-\frac{1}{x}\right)\dx-\ln\varepsilon+\ln a+\gamma\right]=\\
     \frac{\varepsilon^{2}}{12}\left[\ln \left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{a (e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\ln\varepsilon+\ln a+\gamma\right]
\end{multline}

The term $\ln a$ is cancelled by the  and symmetry between $a,b,c$ is restored.
Substituting this approximation into the expression \eqref{eq:23} we obtain 
 the final expression:
\begin{multline}
  \label{eq:3}
 f=-\frac{1}{2(ab+bc+ca)}\left\{\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1}+\right.\\
  \left.+\frac{\varepsilon^{2}}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
      \gamma\right]+\frac{\varepsilon^{2}}{12}\ln \varepsilon\right\} +\mathcal{O}(\varepsilon^{3})
\end{multline}

@@

The expansion  (\ref{eq:3}) can be written as
\begin{equation}
  \label{eq:26}
  f=f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2},
\end{equation}
where the coefficients are
\begin{equation}
  \label{eq:27}
  f_{0}=-\frac{1}{2(ab+bc+ca)}\int_{0}^{a} \int_{0}^{b}\int_{0}^{c}\frac{\dx \dy \dz}{e^{x+y+z}-1},
\end{equation}
\begin{equation}
  \label{eq:28}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:30}
  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12},
\end{equation}
and
\begin{equation}
  \label{eq:29}
  f_{3}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12}\left[\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-
    \gamma\right].
\end{equation}

@@

First two terms $f_{0}$ and $f_{1}$ are interpreted as a bulk and
boundary free energies in the corresponding field theory. Since we have $f_{1}=0$, we can conclude
that boundary tension is zero.
The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as
\begin{multline}
  \label{eq:34}
  f_{0}=\frac{1}{2(ab+bc+ca)}\left[abc + \Li_{3}(e^{a})+\Li_{3}(e^{b})+\Li_{3}(e^{c})-
    \Li_{3}(e^{a+b})\right.\\
  \left.-\Li_{3}(e^{b+c})-    \Li_{3}(e^{a+c})+    \Li_{3}(e^{a+b+c})-\zeta(3)\right]
\end{multline}
Here Riemann zeta function appears as a particular value of polylogarithm $\Li_{3}(1)=\zeta(3)$.

@@

The last term $f_{3}$ depends only on the shape of the domain through $a,b,c$ with a universal
contribution that is equal to the Euler constant $\gamma$. We conjecture that Euler constant will
appear even for a different choice of Kasteleyn weighting, due to the treatment of logarithmic
divergency. In the future work we will consider coordinate dependent values of $q$ and more complex
geometries, as was done in the paper \cite{okounkov2007random}, to check this suggestion.

>>>>

For $\left.f\right|_{\varepsilon\to 0}$ we have $\chi(0)=1$ and the sum $\sum_{n=1}^{\infty}
\frac{H_{n}}{n^{3}}$ is just a sum of  polylogarithms
$\mathrm{Li}_{s}(z)=\sum_{n=1}^{\infty}\frac{z^{n}}{n^{s}}$ of third order:
\begin{multline}
  \label{eq:42}
  \left.f\right|_{\varepsilon\to 0} =\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
    \Li_{3}(e^{-a-b})\right.\\
  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
\end{multline}
Here Riemann zeta function appears as a particular value of polylogarithm $\Li_{3}(1)=\zeta(3)$.

The derivative of the function $\chi(z)$ is zero, $\chi'(0)=0$, and the series
$\sum_{n=1}^{\infty} \frac{\chi'(n\varepsilon)}{n^{2}}H_{n}$ are convergent for a finite
$\varepsilon$, thus we have for a derivative
\begin{equation}
  \label{eq:43}
\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}=0
\end{equation}

@@

First sum in the expression \eqref{eq:46} can be expressed as follows. First, consider second
derivative of $\chi(z)$, separate an exponent and denote what is left by $\xi(z)$:
\begin{equation}
  \label{eq:48}
  \chi''(z)=e^{-z}\frac{e^{2 z} \left(z^2+4 e^z
   \left(z^2-1\right)+e^{2 z} \left(z^2-4
   z+2\right)+4
   z+2\right)}{\left(e^z-1\right)^4}=e^{-z}\xi(z)
\end{equation}
The sum is then rewritten
\begin{equation}
  \label{eq:49}
  \sum _{n=1}^{\infty} \frac{\chi''(n\varepsilon)}{n}=
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(n\varepsilon) =
  \sum_{n=1}^{\infty}\frac{e^{-n\varepsilon}}{n}\xi(0)+  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}   
\end{equation}
The first term is series for the logarithm $\ln\left(1-e^{-\varepsilon}\right)\approx \ln
\varepsilon$,
the second term can approximated by the integral:
\begin{equation}
  \label{eq:50}
  \varepsilon\sum_{n=1}^{\infty}e^{-n\varepsilon}\frac{\xi(n\varepsilon)-\xi(0)}{n\varepsilon}\approx
  \int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
\end{equation}
\begin{equation}
  \label{eq:51}
  \frac{\partial^{2} f}{\partial
  \varepsilon^{2}}\approx-\frac{1}{2(ab+bc+ca)}
\left[\frac{1}{6}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{6}\ln \varepsilon+\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz\right]
\end{equation}
Since we have logarithmic term in the second derivative, we have the behavior of free energy of the form
\begin{equation}
  \label{eq:26}
  f\approx f_{0}+f_{1}\varepsilon +f_{2}\varepsilon^{2}\ln\varepsilon+ f_{3}\varepsilon^{2}+\mathcal{O}(\varepsilon^{3}),
\end{equation}
as expected in general in two-dimensional critical systems \cite{cardy1988finite}. Taking the
derivatives of such expression by $\varepsilon$, we get $f_{0}=f(0)$,
$f_{1}=\left.\frac{\partial f}{\partial \varepsilon}\right|_{\varepsilon\to 0}$,
$\frac{\partial^{2} f}{\partial \varepsilon^{2}}=f_{2}(2\ln\varepsilon+3)+f_{3}$.

Thus we have the coefficients
\begin{multline}
  \label{eq:27}
  f_{0}=\frac{1}{2(ab+bc+ca)}\left[\Li_{3}(e^{-a})+\Li_{3}(e^{-b})+\Li_{3}(e^{-c})-
    \Li_{3}(e^{-a-b})\right.\\
  \left.-\Li_{3}(e^{-b-c})-    \Li_{3}(e^{-a-c})+    \Li_{3}(e^{-a-b-c})-\zeta(3)\right]
\end{multline}

\begin{equation}
  \label{eq:28}
  f_{1}=0,
\end{equation}
\begin{equation}
  \label{eq:30}
  f_{2}=-\frac{1}{2(ab+bc+ca)}\frac{1}{12},
\end{equation}
and
\begin{equation}
  \label{eq:29}
  f_{3}=-\frac{1}{2(ab+bc+ca)}\left[\frac{1}{12}\ln\left(\frac{(e^{a}-1)(e^{b}-1)(e^{c}-1)(e^{a+b+c}-1)}{(e^{a+b}-1)(e^{b+c}-1)(e^{a+c}-1)}\right)-\frac{1}{8}+ \frac{1}{2}\int_{0}^{\infty} e^{-z}\frac{\xi(z)-\xi(0)}{z} dz
    \right].
\end{equation}

@@

@@

First two terms $f_{0}$ and $f_{1}$ are interpreted as a bulk and
boundary free energies in the corresponding field theory. Since we have $f_{1}=0$, we can conclude
that boundary tension is zero.
The value of the first term $f_{0}$ can be rewritten using polylogarithm functions as

@@

The last term $f_{3}$ depends only on the shape of the domain through $a,b,c$ with a universal
contribution that is equal to the integral of a function $e^{-z}\frac{\xi(z)-\xi(0)}{z}$. We conjecture
this constant will appear even for a different choice of Kasteleyn weighting, due to the treatment
of logarithmic divergency. In the future work we will consider coordinate dependent values of $q$
and more complex geometries, as was done in the paper \cite{okounkov2007random}, to check this
suggestion.

\section{Numeric checks}
\label{sec:numeric-checks}
